Who introduced this bug? \\ It may not have been caused by the previous commit!

### 2016-02-01 paperMSR.tex
retocando aqui y alla

\begin{table}[htb]
\begin{center} {\footnotesize
\begin{tabular}{lcc}
\toprule[0.3mm]
  & \multicolumn{1}{c}{One previous } & \multicolumn{1}{c}{More than one previous} \\
  & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commit} \\\hline
\raisebox{1ex}{Cause}     & (65) 50\% & (86) 48\% \\[0ex]
\raisebox{1ex}{Not cause} & (30) 23\% & (82) 46\% \\[0ex]
\raisebox{1ex}{Undecided} & (36) 27\% & (11) ~6\% \\[0ex]
\bottomrule[0.3mm]
\end{tabular} }
\caption{Probability of the cause of the bug when the bug report present one previous commit or more than one previous commit.}
\label{tab:secondStage}
\end{center}
\end{table}

@@

And we are talking about a bug report not a new feature, these kinds of cases use to be when a researcher forgot check some case inside a function.
\begin{enumerate}
\item Is responsible the function where these lines are content?
\item Is responsible the last commit that modify something in the function?
\end{enumerate}

\grex{Puedes elaborar un poco mas el parrafo (y los puntos) anterior(es)? Puede ser en castellano.}
\gema{En casos de que el error se arregle solamente anadiendo lineas, al intentar saber quien es el causante, podemos pensar en que el responsable podria ser el primero que introduce la funcion que olvido tener en cuenta ese caso, o si la funcion en la que se anade el codigo ha sido modificada varias veces pordriamos pensar que el ultimo que modifico la funcion puede ser el causante porue no se dio cuenta que fataba por anadir ese codigo.}

@@

\gema{ con respecto a los previous commits que son varios: las tablas no llegan a ser muy concluyentes y los numeros son bajos; podemos introducir un poco de discusion sobre que podria ser interesante analizar mas y ver si con mas poblacion se repite algun patron y decir exactamente cuantos comits son los responsables en un bug report.}

@@

%The limited sample size of tickets used in this research is the major threat to its validity. %It may happen, that only with 100 seemingly random tickets, there may be a prior unknown tendency. This is in fact similar to~\cite{sliwerski2005changes}, where the trend indicates that most bugs are fixed on Fridays.
The number of the tickets extracted form Launchpad is high, but probably not as high as to state that it can be representative of all free/open source systems, or the software industry. It has not to be forgotten that the analysis requires a lot of human effort, so that achieving large numbers of cases is difficult.

>>>>

\begin{table}[htb]
\begin{center} {\footnotesize
\begin{tabular}{lcc}
\toprule[0.3mm]
  & \multicolumn{1}{c}{One previous } & \multicolumn{1}{c}{More than one previous} \\
  & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commit} \\\hline
\raisebox{1ex}{Cause}     & (65) 50\% & (86) 48\% \\[0ex]
\raisebox{1ex}{Not cause} & (30) 23\% & (82) 46\% \\[0ex]
\raisebox{1ex}{Undecided} & (36) 27\% & (11) ~6\% \\[0ex]
\bottomrule[0.3mm]
\end{tabular} }
\caption{Probability of being the cause of a bug depending on if just one previous commit or more than one previous commits are identified.}
\label{tab:secondStage}
\end{center}
\end{table}

@@

%And we are talking about a bug report not a new feature, these kinds of cases use to be when a researcher forgot check some case inside a function.
%\begin{enumerate}
%\item Is responsible the function where these lines are content?
%\item Is responsible the last commit that modify something in the function?
%\end{enumerate}

%\grex{Puedes elaborar un poco mas el parrafo (y los puntos) anterior(es)? Puede ser en castellano.}
%\gema{En casos de que el error se arregle solamente anadiendo lineas, al intentar saber quien es el causante, podemos pensar en que el responsable podria ser el primero que introduce la funcion que olvido tener en cuenta ese caso, o si la funcion en la que se anade el codigo ha sido modificada varias veces pordriamos pensar que el ultimo que modifico la funcion puede ser el causante porue no se dio cuenta que fataba por anadir ese codigo.}

@@

@@

%The limited sample size of tickets used in this research is the major threat to its validity. %It may happen, that only with 100 seemingly random tickets, there may be a prior unknown tendency. This is in fact similar to~\cite{sliwerski2005changes}, where the trend indicates that most bugs are fixed on Fridays.
The number of the tickets extracted form Launchpad is relatively high, but probably not as high as to state that it can be representative of all free/open source systems, or the software industry. It has not to be forgotten that the analysis requires a lot of human effort, so that achieving large numbers of cases is difficult.
